### 2016-04-20 writing/latex/coincidence.tex
Finish wilf, start appendixes

\section{Equivalence classes of Av(\{321, (21, \textit{R})\}).}
Through expermentation we discover that there are a total of 29 equivalence
classes of mesh patterns with underlying classical pattern \(\perm{2,1}\).

@@

The other reasoning applies to the patterns
\begin{equation*}
    m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } m_2 = \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
\end{equation*}
which are coincident by expermentation.

>>>>

\section{Equivalence classes of Av(\{321, (21, \textit{R})\}).}
Through experimentation we discover that there are a total of 29 equivalence
classes of mesh patterns with underlying classical pattern \(\perm{2,1}\).

@@

The other reasoning applies to the patterns
\begin{equation*}
    m_1 = \pattern{}{1,2}{0/1,0/2,2/0,2/1} \text{ and } m_2 = \pattern{}{1,2}{0/1,0/2,1/1,2/0,2/1}
\end{equation*}
which are coincident by experimentation.

### 2016-04-20 writing/latex/wilf.tex
Finish wilf, start appendixes

The avoiders of the pattern \(p_1 = \textpattern{}{1}{0/1,1/0}\) can be
decomposed around the maximum element in order to give the following
structural decomposition.
\begin{equation*}
    \mathcal{F} = \varepsilon \sqcup \decompmax{0/1,1/0}{\mathcal{F}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}
Since if the upper right section was empty the maximum would create an
occurrence of the pattern, however no points in this section can create
an occurrence since the maximum lies in a region corresponding to the
shading in \(p_1\). The lower right region however can create occurrences
of \(p_1\) and therefore must also avoid \(p_1\) as well as \(\perm{2,3,1}\).
This gives the generating function of avoiders to be the function \(F(x)\)
satisfying.
\begin{equation*}
    F(x) = 1 + xF(x)(C(x)-1)
\end{equation*}

@@

Now we decompose the avoiders of \(m_2\) around the leftmost point
\begin{equation*}
    \mathcal{L}_2 =
    \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}\setminus\varepsilon}
    \sqcup
    \decompleft{0/1,1/0,1/1}{\mathcal{L}_2}{}{}{}
\end{equation*}
This gives us two generating functions satisfying the following pair of equations
\begin{align}
    L_1(x) &= 1 + xC(x)(G(x)-1) +xL_1(x) \label{eqn:genL1}\\
    \text{ and }L_2(x) &= 1 + x(C(x)-1)^2 + xL_2(x) \label{eqn:genL2}
\end{align}
In order for these two functions to give the same value it is necessary to show that
\eqref{eqn:genL1} and \eqref{eqn:genL2} are equal, this occurs if and only if
\(C(x)(G(x)-1) = (C(x)-1)^2\).
\begin{align*}
        (C(x)-1)^2 &= C(x)(G(x)-1)\\
        \shortintertext{Using the definition of \(G\) and \(C\)}
        x^2C^4(x) &=  (1+xC(x))(xC^2(x)-xC(x))\\
        xC^3(x)&=C(x)-1+xC^3(x)-xC^2(x)\\
        0 &= C(x) - 1 -xC^2(x)\\
        C(x) &= 1 +xC^2(x)
\end{align*}
The final line is always satisfied, and therefore the two generating functions
are equal.

@@

Now in \(m_2\) and \(m_4\) containers we can use the same method as in
\eqref{eqn:splitboxes} to separate the two decreasing sequences in the
free boxes in the top row, and the mixing happens in the same manner
as in a container of \(m_3\).
We now have that \(m_2,m_3\) and \(m_4\) have the same number of containers
so are Wilf-equivalent, and that \(m_1\) and \(m_2\) have the same generating
function. So all four classes are Wilf-equivalent.
\subsection{}
The classes containing the following patterns are Wilf-equivalent
\begin{equation*}
    \pattern{}{1,2}{} \text{ and }
    \pattern{}{2,1}{}
\end{equation*}
This is true since the only avoiders of these patterns are the decreasing
sequence and the increasing sequence respectively, and both of these
avoid \(\perm{2,3,1}\) in all cases. There is therefore \(1\) avoider at
every length.

@@

The second pattern occurs if the last element is higher than
the penultimate element. This can only occur if the last element is
in a single block in the set partition context, In order to construct
a avoider of length \(n\) we can take any avoider \(\perm{2,3,1}\)
of length \(n-1\) and insert the new maximum into the last block.
This ensures that the last block is never a singleton. This means
that these permutations are also counted by \(M(x) = 1+xC(x)\).

The avoiders of the third pattern can be decomposed by the maximum
to give
\begin{equation*}
    \mathcal{M}_3 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{F}}{}{}{\mathcal{M}_3}
\end{equation*}
The generating function derived satisfies \(M_3(X) = 1 + xF(x)M_3(x)\).
The fourth pattern can be decomposed around the maximum in a similar
manner.
\begin{equation*}
    \mathcal{M}_4 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{M}_4}{}{}{\mathcal{F}}
\end{equation*}

Finally considering the last pattern, the only way we can construct an
avoider is to take any \(\perm{2,3,1}\) avoider and add a new minimum
at the start of the permutation. Adding a new leftmost point in any other
position would either create an occurrence of \(\perm{2,3,1}\) or the pattern.
Therefore this is also counted by \(M(x) = 1+xC(x)\).
\subsection{}
\begin{equation*}
    p_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    p_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
\end{equation*}
Let \(\mathcal{N}_1\) be the set of avoiders of \(p_1\), by structural decomposition
around the leftmost point we have
\begin{equation*}
    \mathcal{N}_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{N}_1}{}{}{\mathcal{N}^\prime_1}
\end{equation*}
Where \(\mathcal{N}^\prime_1\) is a permutation avoiding \(\perm{2,3,1}, m_1\)
and \(\textpattern{}{1}{0/0,0/1,1/1}\)
Now consider the decomposition of a permutation in \(\mathcal{N}^\prime_1\) it can
once again be decomposed around the leftmost point
\begin{equation*}
    \mathcal{N}^\prime_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{N}_1\setminus\varepsilon}{}{}{\mathcal{N}^\prime_1}
\end{equation*}
This is a complete decomposition of avoiders of \(p_1\). Now we
look at an avoider of \(p_2\), this time decomposition is around the maximum
\begin{equation*}
    \mathcal{N}_2 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{N}_2}{}{}{\mathcal{N}^\prime_2}
\end{equation*}

Again we use the same method of decomposition of a permutation in \(\mathcal{N}^\prime_2\)
\begin{equation*}
    \mathcal{N}^\prime_2 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{N}_2\setminus\varepsilon}{}{}{\mathcal{N}^\prime_2}
\end{equation*}

This gives us a generating function \(N(x)\) satisfying
\begin{align}
    N(x) &= 1 + xN(x)N^\prime(x) \label{eqn:Ngen}\\
    N(x) &= 1 + x(N(x)-1)N^\prime(x)\label{eqn:NprimeGen}
\end{align}

Solving \EquationRef{eqn:NprimeGen} for \(N^\prime(x)\) and substituting into
\EquationRef{eqn:Ngen} gives us the fact that a the generating function for
\(N(x)\) satisfies
\begin{equation}
    N(x) = xN^2(x) - x(N(x) - 1) + 1
\end{equation}

>>>>

The avoiders of the pattern \(p_1 = \textpattern{}{1}{0/1,1/0}\) can be
decomposed around the maximum element in order to give the following
structural decomposition.
\begin{equation*}
    \mathcal{F} = \varepsilon \sqcup \decompmax{0/1,1/0}{\mathcal{F}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}
Since if the upper right section was empty the maximum would create an
occurrence of the pattern, however no points in this section can create
an occurrence since the maximum lies in a region corresponding to the
shading in \(p_1\). The lower right region however can create occurrences
of \(p_1\) and therefore must also avoid \(p_1\) as well as \(\perm{2,3,1}\).
This gives the generating function of avoiders to be the function \(F(x)\)
satisfying.
\begin{align*}
    F(x) &= 1 + xF(x)(C(x)-1) \\
    \shortintertext{Solving for \(F\) gives}
    F(x) &= \frac{1}{1+x-xC(x)}
\end{align*}

@@

Now we decompose the avoiders of \(m_2\) around the leftmost point
\begin{equation*}
    \mathcal{L}_2 =
    \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}\setminus\varepsilon}
    \sqcup
    \decompleft{0/1,1/0,1/1}{\mathcal{L}_2}{}{}{}
\end{equation*}
This gives us two generating functions satisfying the following pair of equations
\begin{align}
    L_1(x) &= 1 + xC(x)(G(x)-1) +xL_1(x) \label{eqn:genL1}\\
    \text{ and }L_2(x) &= 1 + x(C(x)-1)^2 + xL_2(x) \label{eqn:genL2}
\end{align}
In order for these two functions to give the same value it is necessary to show that
\eqref{eqn:genL1} and \eqref{eqn:genL2} are equal, this occurs if
\(C(x)(G(x)-1) = (C(x)-1)^2\).
\begin{align*}
    &&(C(x)-1)^2 &= C(x)(G(x)-1)\\
        &\Leftrightarrow& x^2C^4(x) &=  xC(x)(C(x)-1)C(x) &&\text{By definition of \(G\) and \(C\)}\\
        &\Leftrightarrow& x^2C^4(x)&=xC^3(x)-xC^2(x)\\
        &\Leftrightarrow& xC^2(x) &= C(x) -1 &&\text{Divide by \(xC^2(x)\)}\\
        &\Leftrightarrow& C(x) &= 1 +xC^2(x)
\end{align*}
The final line is always satisfied since it is the form of \(C(x)\), and
therefore the two generating functions are equal.

@@

Now in \(m_2\) and \(m_4\) containers we can use the same method as in
\eqref{eqn:splitboxes} to separate the two decreasing sequences in the
free boxes in the top row, and the mixing happens in the same manner
as in a container of \(m_3\).
We now have that \(m_2,m_3\) and \(m_4\) have the same number of containers
so are Wilf-equivalent, and that \(m_1\) and \(m_2\) have the same generating
function so all four classes are Wilf-equivalent.
\subsection{}
The classes containing the following patterns are Wilf-equivalent
\begin{equation*}
    \pattern{}{1,2}{} \text{ and }
    \pattern{}{2,1}{}
\end{equation*}
This is true since the only avoiders of these patterns are the decreasing
sequence and the increasing sequence respectively, and both of these
avoid \(\perm{2,3,1}\) in all cases. There is therefore \(1\) avoider at
every length.

@@

% If \(\mathcal{M}_2\) is the set of avoiders of
% \textpattern{}{1,2}{1/1,2/1,1/0,1/2,2/0,2/2}, then by structural
% decomposition around the maximum we have
% \begin{equation*}
%     \mathcal{M}_2 = \varepsilon \sqcup
%     \decompmax{0/1,1/0}{\mathcal{C}}{}{}{\scriptstyle\mathcal{M}_1\setminus\varepsilon}
%     \sqcup \tikz{\filldraw (0,0) circle (3pt);}
% \end{equation*}
% Alternatively,
The pattern \textpattern{}{1,2}{1/1,2/1,1/0,1/2,2/0,2/2} occurs if
the last element is higher than the penultimate element. This can only occur
if the last element is in a single block in the set partition context, In order
to construct a avoider of length \(n\) we can take any avoider of
\(\perm{2,3,1}\) of length \(n-1\) and insert the new maximum into the last
block.  This ensures that the last block is never a singleton. This means
that these permutations are also counted by \(M(x) = 1+xC(x)\).

The avoiders of the third pattern can be decomposed by the maximum
to give
\begin{equation*}
    \mathcal{M}_3 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{F}}{}{}{\mathcal{M}_3}
\end{equation*}
The generating function derived satisfies \(M_3(x) = 1 + xF(x)M_3(x)\).
The fourth pattern can be decomposed around the maximum in a similar
manner.
\begin{equation*}
    \mathcal{M}_4 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{M}_4}{}{}{\mathcal{F}}
\end{equation*}

Finally considering the last pattern, the only way we can construct an
avoider is to take any \(\perm{2,3,1}\) avoider and add a new minimum
at the start of the permutation. Adding a new leftmost point in any other
position would either create an occurrence of \(\perm{2,3,1}\) or the pattern.
Therefore this is also counted by \(M(x) = 1+xC(x)\).

We need to show that the generating function \(M_3(x)\) is the same as \(M(x)\)
\begin{equation*}
    \begin{aligned}
        M_3(x) &= 1 + xF(x)M_3(x) \\
        &= \frac{1}{1-xF(x)} && \text{Solving for \(M_3(x)\)}\\
        &= \frac{1}{1 - \frac{x}{1+x-xC(x)}} &&\text{Substituting for \(F(x)\)}\\
        &= \frac{1-xC(x) +x}{1-xC(x)}\\
        &= 1+xC(x)
    \end{aligned}
\end{equation*}
We have that \(M_3(x) = 1+xC(x)= M(x) \) so all four patterns are Wilf-equivalent.

\subsection{}
The patterns
\begin{equation*}
    \begin{aligned}
        m_1 = \pattern{}{1,2}{0/0,0/1,1/0,1/2,2/1} \text{ and }
        m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0}\\
        \text{ and }
        m_3 = \pattern{}{1,2}{0/1,0/2,1/0,1/2,2/0,2/2} \text{ and }
        m_4 = \pattern{}{2,1}{1/0,1/1,2/1,2/2}\\
    \end{aligned}
\end{equation*}
Can be shown to be Wilf-equivalent. First we consider a container of \(m_2\) in \(\av{\perm{2,3,1}}\)
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \fill[pattern=north east lines, pattern color=black!75] (2.5, 1) rectangle +(0.5,1);
        \fill[pattern=north east lines, pattern color=black!75] (2.0, 2) rectangle +(0.5,1);
        \draw (2.5,1) -- (2.5,3);
        \draw (1.5,0.5) node {\(b_1\)};
        \draw (2.25,1.5) node {\(\scriptstyle b_2\)};
        \draw (2.75,2.5) node {\(\scriptstyle b_3\)};
        \modpattern[2]{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0}
    \end{tikzpicture}
    }
\end{equation*}
We can choose the lowest occurrence of \(m_2\) without loss of generality.
The region corresponding to \(b_1\) must avoid the pattern \(\textpattern{}{1}{0/1,1/0}\)
as well as \(\perm{2,1,3}\). The regions corresponding to \(b_2\) and \(b_3\) must
now contain avoiders of \(\perm{2,3,1}\), these regions cannot mix in order to avoid
\(\perm{2,3,1}\). Since we already have an occurrence of
\(m_2\) we do not need to care about creating more occurrences so there are no
other conditions on these boxes.

Now looking at a container of \(m_3\) in \(\av{\perm{2,3,1}}\)
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \fill[pattern=north east lines, pattern color=black!75] (1, 1.5) rectangle +(1,0.5);
        \fill[pattern=north east lines, pattern color=black!75] (2, 1) rectangle +(1,0.5);
        \draw (1,1.5) -- (3,1.5);
        \draw (0.5,0.5) node {\(b_1\)};
        \draw (1.5,1.25) node {\(\scriptstyle b_2\)};
        \draw (2.5,1.75) node {\(\scriptstyle b_3\)};
        \modpattern[2]{}{1,2}{0/1,0/2,1/0,1/2,2/0,2/2}
    \end{tikzpicture}
    }
\end{equation*}
We consider the leftmost occurrence of \(m_3\), the region corresponding
to \(b_1\) must avoid the pattern \(\textpattern{}{1}{0/1,1/0}\) as well as
\(\perm{2,3,1}\) once more. The regions corresponding to \(b_2\) and \(b_3\)
must avoid \(\perm{2,3,1}\) and as in a container of \(m_2\) these regions cannot
mix, as doing so would lead to an occurrence of \(\perm{2,3,1}\).
Therefore both of these sets of containers are enumerated in the same way.

Now we find a structural decomposition for an avoider of \(m_2\).
Decomposing around the maximum we see the set of avoiders of \(m_2\)
have the form
\begin{equation*}
    \mathcal{N}_2 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\scriptstyle\mathcal{N}_2\setminus\varepsilon}{}{}{\mathcal{C}}
    \sqcup
    \decompmax{0/0,0/1,1/0}{}{}{}{\mathcal{F}}
\end{equation*}
We can decompose an avoider of \(m_1\) in \(\av{\perm{2,3,1}}\) around the leftmost point
in a similar manner
\begin{equation*}
    \mathcal{N}_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle\mathcal{N}_1\setminus\varepsilon}{}{}{\mathcal{C}}
    \sqcup
    \decompleft{0/0,0/1,1/0}{}{}{}{\mathcal{F}}
\end{equation*}
These two decompositions tell us that these two patterns are Wilf-equivalent
and have generating function
\begin{equation}
    N_1 = 1 + x(N_1(x)-1)C(x) +xF(x)
    \label{eqn:ngen}
\end{equation}
Now consider an avoider of \(m_4\) decomposed around the maximum
\begin{equation*}
    \mathcal{N}_4 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{O}}
\end{equation*}
Where \(\mathcal{O}\) is the permutations avoiding \(\perm{2,3,1},m_4\) and
\(p = \textpattern{}{1}{0/0,0/1,1/1}\) since if the subsequence in this box
were to start with the maximum then this point and the maximum would create
an occurrence of \(m_4\).
Now consider decomposition of a permutation in \(\mathcal{O}\) around its
leftmost point.
\begin{equation*}
    \mathcal{O} = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{C}}{}{}{\scriptstyle\mathcal{N}_4\setminus\varepsilon}
\end{equation*}
This gives us the generating function
\begin{equation*}
    O(x) = 1 + xC(x)(N_4(x)-1)
\end{equation*}
Now we can construct the following for \(N_4\)
\begin{equation}
    N_4(x) = 1 +xC(x)(xC(x)(N_4(x)-1)+1)
    \label{eqn:ngen2}
\end{equation}

All that remains to show Wilf-equivalence is to show that \EquationRef{eqn:ngen} and
\EquationRef{eqn:ngen2} are the same generating function.
First solve \EquationRef{eqn:ngen2} for \(N_4(x)\)
\begin{equation}
    \begin{aligned}
        N_4(x) &= 1+xC(x)(xC(x)(N_4(x)-1)+1)\\
        &= 1 + x^2C^2(x)N_4(x) -x^2C^2(x) +xC(x)\\
        &= 1 + \frac{xC(x)}{1 - x^2C^2(x)}\\
        &= 1 + \frac{xC(x)}{(1-xC(x))(1+xC(x))} && \text{Difference of squares}\\
        N_4(x)&= 1 + \frac{xC^2(x)}{1+xC(x)} && C(x) = \frac{1}{1-xC(x)}
    \end{aligned}
\end{equation}

Now we solve \EquationRef{eqn:ngen} for \(N_1(x)\)
\begin{equation}
    \begin{aligned}
        N_1(x)&= 1+x(N_1(x)-1)C(x)+xF(x)\\
        &= 1+xN_1(x)C(x)-xC(x)+\frac{x}{1+x-xC(x)} &&\text{Substitution of \(F(x)\)}\\
        N_1(x)(1-xC(x))&= \frac{x^2C^2(x) - (x^2+2x)C(x) + 2x+1}{1+x-xC(x)}\\
        N_1(x) &= \frac{x^2C^2(x) - (x^2+2x)C(x) + x+1+x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 +\frac{x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 + \frac{x}{1-x^2C(x)-xC(x)} && xC^2(x) = C(x)-1\\
        &= 1 + \frac{xC^2(x)}{C^2(x) - xC^3(x)(x+1)}\\
        &= 1 + \frac{xC^2(x)}{C(x) - xC^2(x) + xC(x)} && xC^2(x) = C(x)-1\\
        N_1(x)&= 1 + \frac{xC^2(x)}{1+xC(x)} && C(x) = 1+xC^2(x)\\
    \end{aligned}
\end{equation}
We have shown that \(N_1\) and \(N_4\) are indeed the same generating function,
and we have that the classes containing these four patterns are Wilf-equivalent.

\subsection{}
\begin{equation*}
    m_1 = \pattern{}{1,2}{1/0,1/1,1/2,2/0,2/1} \text{ and }
    m_2 = \pattern{}{2,1}{0/1,1/0,1/1,1/2,2/1}
\end{equation*}
Let \(\mathcal{P}_1\) be the set of avoiders of \(m_1\), by structural decomposition
around the leftmost point we have
\begin{equation*}
    \mathcal{P}_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{P}_1}{}{}{\mathcal{P}^\prime_1}
\end{equation*}
Where \(\mathcal{P}^\prime_1\) is a permutation avoiding \(\perm{2,3,1}, m_1\)
and \(\textpattern{}{1}{0/0,0/1,1/1}\)
Now consider the decomposition of a permutation in \(\mathcal{P}^\prime_1\) it can
once again be decomposed around the leftmost point
\begin{equation*}
    \mathcal{P}^\prime_1 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{P}_1\setminus\varepsilon}{}{}{\mathcal{P}^\prime_1}
\end{equation*}
This is a complete decomposition of avoiders of \(m_1\). Pow we
look at an avoider of \(m_2\), this time decomposition is around the maximum
\begin{equation*}
    \mathcal{P}_2 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\mathcal{P}_2}{}{}{\mathcal{P}^\prime_2}
\end{equation*}

Again we use the same method of decomposition of a permutation in \(\mathcal{P}^\prime_2\)
\begin{equation*}
    \mathcal{P}^\prime_2 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{P}_2\setminus\varepsilon}{}{}{\mathcal{P}^\prime_2}
\end{equation*}

This gives us a generating function \(P(x)\) satisfying
\begin{align}
    P(x) &= 1 + xP(x)P^\prime(x) \label{eqn:Pgen}\\
    P(x) &= 1 + x(P(x)-1)P^\prime(x)\label{eqn:PprimeGen}
\end{align}

Solving \EquationRef{eqn:PprimeGen} for \(P^\prime(x)\) and substituting into
\EquationRef{eqn:Pgen} gives us the fact that a the generating function for
\(P(x)\) satisfies
\begin{equation}
    P(x) = xP^2(x) - x(P(x) - 1) + 1
\end{equation}

\subsection{}
\begin{gather*}
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/2},
        \pattern{}{1,2}{0/1,0/2,1/0,1/1,1/2,2/0,2/2},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/0},\\
        \pattern{}{1,2}{0/0,0/1,0/2,1/2,2/0,2/1,2/2},
        \pattern{}{1,2}{0/0,0/1,0/2,1/1,1/2,2/0,2/2},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
\end{gather*}

In order to gain enumeration, consider decomposition of avoiders
of \(\textpattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/2}\) around
the maximum.
\begin{equation*}
    \mathcal{Q}_1 = \varepsilon \sqcup
    \tikz{\filldraw (0,0) circle (3pt);}
    \sqcup
    \decompmax{0/1,1/0}{\mathcal{C\setminus\varepsilon}}{}{}{\mathcal{C}}
\end{equation*}

This gives us the following generating function
\begin{equation}
    Q(x) = 1 + x + xC(x)(C(x)-1) \label{eq:qgen}
\end{equation}

Now we consider decomposition of an avoider
\textpattern{}{1,2}{0/1,0/2,1/0,1/1,1/2,2/0,2/2} around the maximum,
this avoider must fit into the following form
\begin{equation*}
    \mathcal{Q}_2 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{G}_2}{}{}{\mathcal{C}}
\end{equation*}
This gives us the generating function
\begin{equation*}
    \begin{aligned}
        Q_2(x) &= 1+xC(x)G(x)\\
        &= 1+xC(x)(1+xC(x)(C(x)-1))\\
        &= 1 +xC(x)(C(x)-xC(x)) && C(x) = 1+xC^2(x)\\
        &= 1 +x + xC^2(x) - xC(x) \\
        &= 1 +x + xC(x)(C(x)-1)
    \end{aligned}
\end{equation*}
Therefore this generating function is the same as \EquationRef{eq:qgen}.
We can decompose
\textpattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/1},
\textpattern{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0,2/1},
\textpattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/0},
\textpattern{}{1,2}{0/0,0/1,0/2,1/2,2/0,2/1,2/2},
and \textpattern{}{1,2}{0/0,0/1,0/2,1/1,1/2,2/0,2/2} around the leftmost point
into an avoider of one of the patterns with generating function \(G(x)\) and
an avoider of \(\perm{2,3,1}\).

Now decompose an avoider of \textpattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
around the leftmost point.
\begin{equation*}
    \mathcal{Q}_3 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{Q}\setminus\varepsilon}{}{}{\mathcal{C}}
    \sqcup \decompleft{0/0,0/1,1/0}{}{}{}{\mathcal{G}_3}
\end{equation*}
This gives generating function \(Q_3(x)\) satisfying
\begin{equation*}
    \begin{aligned}
        Q(x) &= 1 +xC(x)(P(x)-1) + xG(x)\\
        &= C(x) - xC^2(x) + xC(x) +x^2C^3(x) - x^2C^2 && \text{Solving for \(Q(x)\)}\\
        &= 1 + xC(x) +x^2C^3(x)-xC^2(x) && C = 1+xC^2(x)\\
        &= 1 + x + x^2C^3(x) && xC^2(x) = C(x)-1\\
        &= 1 + x + xC(x)(C(x)-1)
    \end{aligned}
\end{equation*}
This is equivalent to \EquationRef{eq:qgen}, and therefore
the classes containing all of these patterns are Wilf-equivalent.
